An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-05-31 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

%
%%%To select an optimal combination of components from a PV system to meet sizing constraints, 
%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
%The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
%Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC). Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
\subsection{Stand-alone PV System Optimization Technique}
To recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables.

@@

\subsection{Assumptions and Premises}

%---------------------------------------------------------------------------
\section{RESULTS AND DISCUSSION}
\label{sec:Results}
%---------------------------------------------------------------------------
\textbf{Case studies.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.

>>>>

During the PV system design, one of the most important aspects to ensure power system security is to analyze power supply availability. The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand. A reliable power is a generation system that has sufficient power to feed load demand in a period.

There are different methods to express system reliability, the most popular are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}. In both methods, if the probability is zero, then the load will always be fulfilled; while in the opposite (probability of one) then the load will never be fulfilled.

LOLP is the probability for the case when a load demand exceeds the generation power by the PV system. And we say that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span. On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand. The main approaches to LPSP demand chronological simulation or probabilistic technique. In both, time series data is necessary, and dynamic behavior analysis. Data is not always available and dynamic analysis is complex, and this is a drawback.

Related to economic analysis, there are several methods available. The aim is to determine wheter the project has or has not acceptable investment, and the usual is to perform economic analysis after reliability analysis in order to propose a system with high reliability and lowest cost~\cite{Alsadi2018}. Frequently are used the Net Present Cost (NPC), the Levelized Cost of Energy (LCOE), or the Life Cycle Cost (LCC).

NPC is the total present value of a time series. The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an interest rate of internal rate of return (IRR).[90]

LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost is considered [91]. LCOE method is useful in comparing different generation technologies with different operating characteristics [6].

LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value [92]. Eq.~\ref{eq:LCC} is used to calculate LCC of a PV system,

\begin{equation}
\label{eq:LCC}
LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
\end{equation}

\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs in present worth.

%
%%%To select an optimal combination of components from a PV system to meet sizing constraints, 
%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
%The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
%Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC). Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
\subsection{Stand-alone PV System Optimization Technique}
To recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables. As number of optimization variables increases, the computation effort will exponentially increase [6]. Hence, to obtain the best PV system design as well as simplified sizing process, past work introduced three main techniques for system sizing calculation [???], namely intuitive, numerical, and analytical methods.

Intuitive method is simple, easy to be implemented, and can be used to give rough suggestion for preliminary design. The sizing rules are based on designer's experience, using lowest performance either in a time period data or by directly using average value (daily, monthly, or annual) of solar irradiance. This method do not the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.

Numerical method the design is simulated for each time step within a period. State of charge of batteries is calculated and investigated. It is very accurate, however is complex, demanding more time for calculation.

Analytical methods is used to obtain a close relation of correlation in a form of equation between capacities and reliabilities. The sizing task become much simpler, however the relation cannot be applied at different sites, because is specific to one specific place of deployment of the PV system, demanding adaptation if another site is analyzed.

@@

\subsection{Assumptions and Premises}
Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. The usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). However, based on the fact that here we are neither considering site characteristics nor the load changes over time, which demands historical data, the reliability analysis will be developed only by the critical period method of PV sizing.

%---------------------------------------------------------------------------
\section{RESULTS AND DISCUSSION}
\label{sec:Results}
%---------------------------------------------------------------------------
\textbf{Case studies.} We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
